Domestic cooking and likelihood

### 2020-01-07 inst/cook.Rmd
consistency check

So the support for our alternative hypothesis would be

>>>>

[as a consistency check we can perform the same calculation with a
slightly different value for `small`:

```{r}
small <- 2e-4  # cf 1e-4 previously
ML_constrained <- maxp(Htot,startp=rep(0.2*(1-small*2.1),5),fcm=c(1,1,1,1,1),fcv=1-2*small)
loglik(indep(ML_constrained),Htot) # cf -29.973 previously
```

and we can see that this is almost the same].  Thus, the support for
our alternative hypothesis would be
